LCS Tool — An Algorithmic Introduction to Lagrangian Coherent Structures

### 2014-02-18 main.tex
Remove newline in middle of paragraph
Add m-file to produce ocean demo figures

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{graphics/ocean_dataset/hyperbolic_shearline_lcs_details_strainline}
\end{center}
\caption{Lambda-line LCSs (green) and strainline LCSs (red) of the ocean data set. Background gray-scale is the finite time Lyapunov exponent. Dashed green lines are Poincare sections. White dots indicate $\lambda_2$ local maxima used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{graphics/ocean_dataset/hyperbolic_shearline_lcs_details_stretchline}
\end{center}
\caption{Lambda-line LCSs (green) and stretchline LCSs (blue) of the ocean data set. Background gray-scale is the finite time Lyapunov exponent. Dashed green lines are Poincare sections. White dots indicate $\lambda_1$ local minima used for stretchline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details stretchline}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_strainlines}
\end{center}
\caption{Lambda-line LCSs (green) and strainline LCSs (red) of the ocean data set. Background gray-scale is the finite time Lyapunov exponent. Dashed green lines are Poincare sections. White dots indicate $\lambda_2$ local maxima used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_stretchlines}
\end{center}
\caption{Lambda-line LCSs (green) and stretchline LCSs (blue) of the ocean data set. Background gray-scale is the finite time Lyapunov exponent. Dashed green lines are Poincare sections. White dots indicate $\lambda_1$ local minima used for stretchline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details stretchline}
\end{figure}
